%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt,margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage{multicol}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}
\setlength{\columnsep}{-0.5in}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{Pranav Ganorkar}
\end{center}
\vspace{-2mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-7mm}
\begin{center}
    \hspace{-\hoffset}
    \href{http://pranavg189.github.io/}{Homepage} ~\textbullet~ \ \href{mailto:pranavg189@gmail.com}{Email} ~\textbullet~ \ \href{https://github.com/pranavg189}{GitHub} ~\textbullet~ \ \href{https://www.linkedin.com/in/pranavganorkar/}{LinkedIn} ~\textbullet~ \ \href{https://pranavganorkar.wordpress.com/}{Blog} ~\textbullet~ \(+91\)-9923798164
\end{center}
\vspace{-7mm}
\begin{resume}


%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\vspace{8mm}

\textbf{Cloud Support Associate - Amazon Web Services} \hfill November 2017 - Present\\
Working on developing AWS Config rules in Python for security, compliance and Auditing as part of Proserv RCS Flex team.
Wrote Python script for AWS Redshift to allow end to end schema migration from an unencrypted cluster to a uncrypted cluster. Handling AWS Premium support cases related to MySQL\textbackslash Aurora MySQL as part of Database support team.

\vspace{2mm}

\textbf{Google Summer of Code (GSoC) Intern - GNOME} \hfill May 2017 - August 2017\\
Made various enhancements to the user interface of GNOME Logs and implemented a shell search provider module to expose search results to other components of GNOME Desktop Suite such as GNOME Shell.

\vspace{2mm}

\textbf{Google Summer of Code (GSoC) Intern - GNOME} \hfill May 2016 - August 2016\\
Interned under Google Summer of Code program with GNOME Foundation. The project was about improving the search functionality in GNOME Logs. GNOME Logs is an open source software to view and organize the logs generated by the journald daemon in a Linux OS using systemd as init system. Worked on moving the search functionality from frontend to backend and made various improvements to the user interface related to search functionality.

\vspace{2mm}

\textbf{Software Engineering Intern - IIT Bombay} \hfill May 2015 - August 2015\\
Involved in developing a web app named ‘RuralIVRS’, a web app for administering an IVRS System to help the NGO's sell rural farmer products to the consumers in the cities. Spring Framework was used as backend and AngularJS on the frontend. Wrote full stack code for various functionalities of the web app. The project was mentored by Prof. Ganesh Ramakrishnan, CSE Dept., IIT Bombay.



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\vspace{8mm}
\textbf{B.E. in Computer Engineering, Graduation Year: 2017} \\
V.E.S Institute of Technology (VESIT), Mumbai University \\
CGPA : \textbf{8.05} (on a scale of 10)

%----------------------------------------------------------------------------------------
%   RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant Courses}
\vspace{8mm}
\begin{multicols}{3}
    \begin{itemize}
      \item Data Structures
      \item Algorithms
      \item Operating Systems
      \item Computer Networks
      \item Cloud Computing
      \item Distributed Systems
      \item Artificial Intelligence
      \item Machine Learning
      \item Human Computer Interaction
    \end{itemize}
\end{multicols}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\vspace{8mm}
\textbf{Languages} - C, Java, Python \\
\textbf{Tools/Frameworks} - Spring, GTK+, Glib, Git, GitHub, MySQL

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Projects}
\vspace{10mm}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
 \item Developed an \textbf{``American Sign Language Recognition System''} based on Deep learning and Computer Vision involving Convolutional Neural Networks (CNN) as a part of my final year project and was implemented using the Keras and TensorFlow libraries.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}
\vspace{12mm}
\begin{itemize}[leftmargin=*]
\item Ranked \textbf{4th} among 5000 students from all over India in IITBombayX Internship contest conducted by Prof. Deepak B. Phatak, CSE Dept., IIT Bombay.
\end{itemize}

%----------------------------------------------------------------------

\end{resume}
\end{document}